%\documentclass[12pt,preprint]{aastex}
\documentclass[12pt,preprint]{emulateapj}
\usepackage{graphicx}

\shorttitle{The PARAS Precision RV Spectrograph}
\shortauthors{Chakraborty et al.}
\slugcomment{Submitted for publication in PASP}
%\received{2010 July 1}

\begin{document}

\title{The Stabilized High Resolution PARAS Echelle Spectrograph: Instrument Description \& First Light Radial Velocity Results}

\author{
  Abhijit Chakraborty\altaffilmark{1},
  Suvrath Mahadevan\altaffilmark{2,3},
  Arpita Roy\altaffilmark{2,3},
  Eric Harvey Richardson\altaffilmark{4}
  F. M. Pathan\altaffilmark{1},
  Vishal Shah\altaffilmark{1},
  Rohit Deshpande\altaffilmark{2,3},
  Priyanka Chaturvedi\altaffilmark{1},
  Rajesh Shah\altaffilmark{1},
  V. Venkatramany\altaffilmark{5}
}
\email{abhijit@prl.res.in}
\altaffiltext{1}{Division of Astronomy ,
  Physical Research Laboratory, Navrangpura, Ahmedabad 380015, India}
\altaffiltext{2}{Department of Astronomy and Astrophysics,
  Pennsylvania State University, 525 Davey Laboratory, University
  Park, PA 16802}
\altaffiltext{3}{Center for Exoplanets \& Habitable Worlds,
  Pennsylvania State University, 525 Davey Laboratory, University
  Park, PA 16802}
\altaffiltext{5}{Aditya High Vaccum Private Limited, Ahmedabad- 280015, India}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}


\end{abstract}

\keywords{planetary systems -- techniques: photometric -- techniques:
  radial velocities -- stars: individual (47 UMa)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{introduction}
\indent The number of known exoplanets planets has growing rapidly in the last decade, with over 550 confirmed exoplanets known to date\footnote{exoplanet.eu}, with most of these confirmed planets having been discovered using radial velocity technique.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation for a Highly Stablized  Spectroscopic Capability on the Mt Abu 1.2m Telescope}
\label{motivation}
\subsection{The Mt Abu 1.2 m Telescope}
\subsection{ The PARAS Project}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparision with other optical precision RV spectrographs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PARAS: Optical Design \& Components}
\label{optdesign}
Blah Blah Blah top level, white pupil design blah blah blah. Optical design Figure. Point to Appendix for a Zemax file description.
\subsection{Fiber Feed, Input optics, and scrambler}
\subsection{OAP Collimators}
\subsection{Grating}
\subsection{Prism}
\subsection{Camera}
\subsection{CCD}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mechanical Design \& Vaccum Enclosure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Environmental Control: Temperature \& Pressure}
\subsection{Temperature Control \& Performance}
\subsection{Vacuum Chamber Stability \& Performance}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Spectral Format, Simultaneous Wavelength Covergage, \& Resolution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cassegrain Feed and Calibration Unit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Efficiency}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Analysis Pipeline}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations \& First Light RV Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ongoing \& Future Upgrades to Enhance RV precision}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}
Funding for PARAS is provided by the Department of Space, Government of India through the Physical Research Laboratory.
We are grateful to Fransico Pepe, Christophe Lovis, Stepehen Udry, and Larry Ramsey for detailed discussions over the years on aspects of building precision RV spectrographs.
This work was partially supported by funding from the Center for Exoplanets and Habitable Worlds. The
Center for Exoplanets and Habitable Worlds is supported by the
Pennsylvania State University, the Eberly College of Science, and the
Pennsylvania Space Grant Consortium.  This work made use of the
SIMBAD database (operated at CDS, Strasbourg, France), NASA's
Astrophysics Data System Bibliographic Services, and the NASA Star and
Exoplanet Database (NStED).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{}


\end{thebibliography}


\end{document}